\bf Service Chain Placement in SDNs \thanks{ A preliminary version appeared in the 3rd International Workshop on Algorithmic Aspects of Cloud Computing (ALGOCLOUD), 2017. Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2019-03-12 src/chain.tex
all comments

Lukovszki and Schmid~\cite{LukovszkiSchmid15} studied the problem of
admission control and placement of service chains, where each chain is
associated with a source-destination pair and is supposed to be routed
via an ordered sequence of $\ell$ VNFs.  The VNFs may have multiple
instantiations, but each node has a limited capacity that bounds the
number of requests it may service.
%
They presented an $O(\log \ell)$-competitive algorithm for the problem
of maximizing the number of serviced chains, assuming that capacities
are $\Omega(\log \ell)$.
%at least logarithmic in $\ell$.
It is also shown that this ratio is asymptotically optimal even for
randomized online algorithms.  APX-hardness results for the offline
version of the problem were also presented.
%
Rost and Schmid~\cite{RostSchmid16} considered variant of this
problem, where each node can host a subset of the VNFs.  In addition,
each VNF has a demand and each VNF-node pair has a capacity, and in a
feasible solution the total demand for each pair is bounded by the
capacity.  They considered two goals: maximum profit and minimum
resource cost and gave bicriteria approximation algorithms which are
based on LP-rounding for several special cases.

@@

@@

>>>>

Lukovszki and Schmid~\cite{LukovszkiSchmid15} studied the problem of
admission control and placement of service chains, where each chain is
associated with a source-destination pair and is supposed to be routed
via an ordered sequence of $\ell$ VNFs.  The VNFs may have multiple
instantiations, but each node has a limited capacity that bounds the
number of requests it may service.
%
They presented an $O(\log \ell)$-competitive algorithm for the problem
of maximizing the number of serviced chains, assuming that capacities
are $\Omega(\log \ell)$.
%at least logarithmic in $\ell$.
It is also shown that this ratio is asymptotically optimal even for
randomized online algorithms.  APX-hardness results for the offline
version of the problem were also presented.
%
Rost and Schmid~\cite{RostSchmid16} considered variant of this
problem, where each node can host a subset of the VNFs.  In addition,
each VNF has a demand and each VNF-node pair has a capacity, and in a
feasible solution the total demand for each pair is bounded by the
capacity.  They considered two goals: maximum profit and minimum
resource cost and gave bicriteria approximation algorithms which are
based on LP-rounding for several special cases.
%
\fix{Sahhaf et al.~\cite{SAHHAF2015492} studied a generalization of the Virtual Network Embedding
Problem where each network function can be decomposed into multiple network function graphs.
They proposed two novel approaches to use service
decompositions at the time of service embedding (i) an
ILP-based algorithm that finds an optimal embedding and (ii) a heuristic-based algorithm to cop with the scalability issues of the first algorithm.}

@@

\begin{proof}
  \fix{From the above discussions it follows that the algorithm finds an optimal robust embedding with respect to c', using Lemma~\ref{lemma:guess} we know that its cost is at most $(1 + \varepsilon)$ times the cost of the optimal robust embedding, for every $\varepsilon > 0$.}
\end{proof}

@@

\section{Conclusion}
\fix{%
Network service chaining is a service concept which has gained much interest from both practitioners and researchers, it promises increased flexibility and cost-efficiency for future carrier networks. 
In this model clients request high level services from the network provider which translate into a service chain that need to be embedded into the physical network.
To ensure efficient utilization of the underline physical network relaible algorithms are needed.
}

\fix{%
In this paper we propose an efficient algorithm that finds an optimal embedding for a single request.
This algorithm works, however, only when the underline network is acyclic.
For general networks we propose an algorithm that finds an optimal embedding with a running time that depends on the topology of the network, more specifically on the number of nodes in the network with more than two connections.
We also propose a heuristic that improves the running time of the last algorithm, for cactus networks, for example, this heuristic is guaranteed to run in polynomial time.
}

\fix{%
Some questions regarding service chain placement remain open. 
Some of these questions are (i) how should we handle multiple (concurrent) requests? (ii) can we find better solutions if we allow embedding a service chain on a walk instead of a path? (iii) is there an efficient (approximation) algorithm that works on real world networks?\footnote{As even the feasibilty problem for general networks is NP-hard some further assumptions need to be made in order to answer this question affirmatively.}
We believe that our results and techniques can serve as a starting point for future work dealing with those questions.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
